Ecological validity of detecting data fabrication in experimental studies.

### 2016-05-14 submission/manuscript.Rmd
Forgot a square, also in the prereg... :-( Did not forget it in the formula after though!
First run at data analysis

$\tilde{s}_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
<!--- \limits^k_{j=1} --->

@@

<!---
### Results.

>>>>

$\tilde{s}^2_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
<!--- \limits^k_{j=1} --->

@@

### Results.
```{r prep data study 1, echo = FALSE}
options(digits = 20)
# Compute the summary statistics for Many Labs
source('../functions/compute_summary_anch_ml.R')
# Process the collected, fabricated data
source('../functions/process_qualtrics_anch_01.R')

# Read the data
ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
ml$stat_know <- NA
ml$spss <- NA
ml$rcran <- NA
ml$stata <- NA
ml$sas <- NA
ml$matlab <- NA
ml$python <- NA
ml$other <- NA
ml$nopro <- NA
ml$noanch <- NA
ml$rng <- NA
ml$full <- NA
ml$tries <- NA
ml$descr <- NA
ml$bonus <- NA
ml$type <- 'ml'
qualtrics$type <- 'qualtrics'

dat <- rbind(qualtrics, ml)
```

```{r compile results for detecting data fabrication, echo = FALSE}
# conduct the analyses iteratively
for (pp in unique(dat$referrer))
{
  # Loop through each study to compute the ANOVA results
  for (j in 1:4)
  {
    study_nr <- j    
    indexor <- dat$referrer == pp & dat$study == study_nr

    harm_mean <- 4^2/(sum(1/dat$anch_n[indexor]))
    male_mean <- mean(dat$anch_m[indexor & dat$partgender == 0])
    female_mean <- mean(dat$anch_m[indexor & dat$partgender == 1])
    control_mean <- mean(dat$anch_m[indexor & dat$anchoring == 0])
    exp_mean <- mean(dat$anch_m[indexor & dat$anchoring == 1])

    ss_error <- sum((dat$anch_n[indexor] - 1) * dat$anch_sd[indexor]^2)
    ss_gender <- (harm_mean * var(c(male_mean, female_mean))) / 2
    ss_condition <- (harm_mean * var(c(control_mean, exp_mean))) / 2
    ss_interaction <- harm_mean * var(dat$anch_m[indexor]) * 3/4 - ss_gender - ss_condition
    ss_total <- ss_error + ss_gender + ss_condition + ss_interaction

    ms_error <- ss_error / (sum(dat$anch_n[indexor]) - 4)
    ms_gender <- ss_gender / (2 - 1)
    ms_condition <- ss_condition / (2 - 1)
    ms_interaction <- ss_interaction / 1

    dat$f_gender[indexor] <- ms_gender / ms_error
    dat$df1_gender[indexor] <- 2 - 1
    dat$df2_gender[indexor] <- sum(dat$anch_n[indexor]) - 4
    dat$p_gender[indexor] <- pf(q = ms_gender / ms_error,
                                df1 = 2 - 1,
                                df2 = sum(dat$anch_n[indexor]) - 4,
                                lower.tail = FALSE)

    dat$f_condition[indexor] <- ms_condition / ms_error
    dat$df1_condition[indexor] <- 2 - 1
    dat$df2_condition[indexor] <- sum(dat$anch_n[indexor]) - 4
    dat$p_condition[indexor] <- pf(q = ms_condition / ms_error,
                                   df1 = 2 - 1,
                                   df2 = sum(dat$anch_n[indexor]) - 4,
                                   lower.tail = FALSE)

    dat$f_interaction[indexor] <- ms_interaction / ms_error
    dat$df1_interaction[indexor] <- 1
    dat$df2_interaction[indexor] <- sum(dat$anch_n[indexor]) - 4
    dat$p_interaction[indexor] <- pf(q = ms_interaction / ms_error,
                                     df1 = 1,
                                     df2 = sum(dat$anch_n[indexor]) - 4,
                                     lower.tail = FALSE)
  }

  sel <- dat$referrer == pp

  # Variance analysis
  # Standardizing the sds

  # Study 1
  sel1 <- dat$referrer == pp & dat$study == 1
  ms_w_1 <- sum((dat$anch_n[sel1] - 1) * dat$anch_sd[sel1]^2) / sum((dat$anch_n[sel1] - 1))
  tilde_s2_1 <- dat$anch_sd[sel1]^2 / ms_w_1
  # Study 2
  sel2 <- dat$referrer == pp & dat$study == 2
  ms_w_2 <- sum((dat$anch_n[sel2] - 1) * dat$anch_sd[sel2]^2) / sum((dat$anch_n[sel2] - 1))
  tilde_s2_2 <- dat$anch_sd[sel2]^2 / ms_w_2
  # Study 3
  sel3 <- dat$referrer == pp & dat$study == 3
  ms_w_3 <- sum((dat$anch_n[sel3] - 1) * dat$anch_sd[sel3]^2) / sum((dat$anch_n[sel3] - 1))
  tilde_s2_3 <- dat$anch_sd[sel3]^2 / ms_w_3
  # Study 4
  sel4 <- dat$referrer == pp & dat$study == 4
  ms_w_4 <- sum((dat$anch_n[sel4] - 1) * dat$anch_sd[sel4]^2) / sum((dat$anch_n[sel4] - 1))
  tilde_s2_4 <- dat$anch_sd[sel4]^2 / ms_w_4

  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))

  iter <- 100000
  s2 <- dat$anch_sd[dat$referrer == pp]^2
  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
  ms_w <- c(rep(ms_w_1, 4), rep(ms_w_2, 4),
            rep(ms_w_3, 4), rep(ms_w_4, 4))
  sim_sigma <- NULL

  for (z in 1:16)
  {
    sim_sigma <- cbind(sim_sigma, ((rchisq(n = iter, df = n_min_1[z]) *  s2[z]) / n_min_1[z]) / ms_w[z])
  }

  sim_sigma_sd <- apply(sim_sigma, 1, sd)

  dat$variance_sd_p[sel] <- sum(sim_sigma_sd < obs_sigma_sd) / iter

  # Compute the Fisher method p-values 
  # for gender and interaction

  # Safety check to make sure there are 4 unique values
  # Iteratively made exceptions for the cases that do not
  if (length(unique(dat$p_gender[sel])) < 4 | 
      # length(unique(dat$p_condition[sel])) < 4 |
      length(unique(dat$p_interaction[sel])) < 4)
  {
    if (pp == 'R_6opw4qQURhqxT3D')
    {
      p_gender <- rep(1, 4)
    } else
    {
      stop(sprintf('Something wrong with the number of p-values available for %s',
                   pp))
    }
  } else 
  {
    p_gender <- unique(dat$p_gender[sel])  
  }

  dat$gender_fish[sel] <- -2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05))))
  dat$gender_fish_df[sel] <- 2 * length(p_gender)
  dat$gender_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05)))),
                                   df = 2 * length(p_gender),
                                   lower.tail = FALSE)

  p_interaction <- unique(dat$p_interaction[sel])
  dat$interaction_fish[sel] <- -2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05))))
  dat$interaction_fish_df[sel] <- 2 * length(p_interaction)
  dat$interaction_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05)))),
                                        df = 2 * length(p_interaction),
                                        lower.tail = FALSE)
}

dat_summary <- dat[ , -which(names(dat) %in% c("study",
                                               "partgender",
                                               "anchoring",
                                               "anch_n",
                                               "anch_m",
                                               "anch_sd",
                                               "f_gender",
                                               "df1_gender",
                                               "df2_gender",
                                               "p_gender",
                                               "f_condition",
                                               "df1_condition",
                                               "df2_condition",
                                               "p_condition",
                                               "f_interaction",
                                               "df1_interaction",
                                               "df2_interaction",
                                               "p_interaction"))]
dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
dat_summary$fish_combine <- -2 * (log(dat_summary$variance_sd_p) + log(dat_summary$gender_fish_p) + 
        log(dat_summary$interaction_fish_p))
dat_summary$fish_combine_p <- pchisq(q = dat_summary$fish_combine,
                                     df = 2 * 3, lower.tail = FALSE)

write.csv(dat_summary,
          'test.csv', row.names = FALSE)
```

```{r inspect results to detect data fabrication, echo = FALSE}

```

<!---

library(ROCR)
data(ROCR.simple)
pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels)
perf <- performance(pred,"tpr","fpr")
plot(perf)
